Meritocracy Scale: Preferences and Perceptions

### 2019-11-21 index.Rmd
update211119

---
title: "Pre-reg, scale perception meritocracy"
author:
- Luis Maldonado
- Juan Carlos Castillo
- Julio Iturra
- Jorge Atria
- Francisco Meneses
date: "13-11-2019"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    toc_depth: 2
    number_sections: false
---

@@

@@

To measure the ideals of meritocracy, it is essential to differentiate preferences (i.e. what is considered desirable) and perceptions (i.e. how reality is believed to be) (duru-bellat, 2012). This work focuses on the perceptions of meritocracy.

Although a group of authors has measured the perception of meritocracy as if the perception of inequality of opportunities were the  side opposite of the continuum (Kunovich, 2007; Newman, 2015), others have shown that both concepts are rather different dimensions(Reynolds , 2014). Following this evidence, we chose to model both constructs as distinct latent variables. Different types of inequalities such as origin, contact or discrimination, cannot be considered in a single factor, since they refer to different realities and perceptions, therefore, it is consistent that they are independent latent variables. We also consider the existence of a latent second order variable, referring to the belief of inequality of opportunities in general.

@@

Additionally, it is important to mention that we will exploratoryly test the relationship between the “get a head” questions and questions that refer to whether “In Chile, people are rewarded or manage to succeed according to different qualities (i.e., hardworking, talented, with contacts)”.

* H1. The perception of meritocracy is a factor in the drift of the importance attributed to talent and the effort to get ahead in life.
* H2. The factors of family origin, contacts and discrimination are grouped into a second order factor that relates to non-meritocratic perceptions.
* H3. Preferences are also grouped into meritocratic and non-meritocratic preferences.
* H4 (exploratory) the way in which the perception of inequality of opportunities is asked influences the perception declared by the interviewees.

@@

The present study is of an observational type focused on the measurement of the meritocracy preception variable. This study is part of an experimental study, applied online, which will be longitudinal panel type, that is, the same subjects will be surveyed 3 different occasions. The subjects will be randomly selected to be assigned to a placebo or to either of the two experimental procedures (change of poverty in Chile or international comparison of inequality)
To access the cases we turn to the Netquest survey company, which has coverage in several Latin American countries.

@@

The Sample that will be necessary for this study has not yet been produced, nor has it begun its field work. However, in order to test the online questionnaire and the functionality of the quota offered by the Qualtrics platform, two previous studies have been carried out. The subjects participated in these two opportunities are excluded to the central sample, which corresponds to the 3-wave panel study.
These data from the two pilot studies were used for methodological decisions, descriptive stadistics, correlations and confirmation tests.
Due to the above, although the definitive sample has not yet been produced and therefore has not been explored, it is responsible to say, in addition to the review of previous research and international databases, it has some notions of the relationship among the variables product of the analysis of the previous samples

@@

# Variables to use:
The variables used for the perception factor of meritocracy are:

* Para surgir en la vida, ¿cuán importante cree
usted que es?
    + Tener ambición
    + El trabajo duro

On the other hand, the questions related to inequality of opportunities are:

* Para surgir en la vida, ¿cuán importante cree
usted que es?
    + provenir de una familia rica o con muchos recursos
    + Tener padres con altos niveles de educación
    + Conocer a las personas adecuadas
    + Tener contactos políticos
    + La raza u origen étnico de las personas
    + El sexo de las personas, ser hombre o mujer

The items of preferences are:

* ¿En qué medida se encuentra usted de acuerdo o en desacuerdo con cada una de las siguientes afirmaciones?
    + Quienes más se esfuerzan deberían obtener mayores recompensas que quienes se esfuerzan menos
    + Quienes poseen más talento deberían obtener mayores recompensas que quienes tienen menos talento
    + Está bien que quienes tienen padres ricos salgan adelante
    + Está bien que quienes tienen buenos contactos salgan adelante

The questions that will be used for the exploratory analysis indicated are:

* ¿En qué medida se encuentra usted de acuerdo o en
desacuerdo con cada una de las siguientes
afirmaciones? En Chile,
    + Quienes más se esfuerzan logran obtener mayores recompensas.
    + Quienes tienen más talento logran obtener mayores recompensas.
    + Las personas con padres ricos logran salir adelante.
    + Los que tienen buenos contactos logran salir adelante.

@@

# Analysis plan
To evaluate these hypotheses, confirmatory factor analysis will be used, since we have strong theory regarding the ordering of the factors. In addition, exploratory factor analysis will be used to evaluate the exploratory hypothesis indicated. The Lavaan R package will be used.

### Inference criteria,
The values that will be used as evaluation criteria for the goodness of the adjustment of the model were taken from the proposal of Ruiz, Partdo and San Martin (2010) and are the following:
*Chi-square:> 0.05
*Chi-square ratio:> 3
*Comparative adjustment goodness index (CFI):> 0.95
*Tucker-Lewis Index (TLI):> 0.95
*Root of the average squared residual approximation <0.08.

@@

### Ethics. JI
The experiment and survey instruments are approved by the IRB of the University of Chile.

# bibliography

Ruiz, M., Pardo, A. & San Martín, R. (2010). Modelos de Ecuaciones Estructurales. -Papeles del psicólogo, 31-(1), pp. 34-45.

Duru-Bellat, M., & Tenret, E. (2012). Who’s for Meritocracy? Individual and Contextual Variations in the Faith. Chicago Journal, 56(2), 223-247.

Kunovich, S., & Slomczynski, K. M. (2007). Systems of Distribution and a Sense of Equity: A Multilevel Analysis of Meritocratic Attitudes in
Post-industrial Societies. European Sociological Review, 23(5), 649–663. doi:10.1093/esr/jcm026

Newman, B. J., Johnston, C. D., & Lown, P. L. (2014). False Consciousness or Class Awareness? Local Income Inequality, Personal Economic Position, and Belief in American Meritocracy. American Journal of Political Science, 59(2), 326-340. doi:10.1111/ajps.12153

Reynolds, J., & Xian, H. (2014). Perceptions of meritocracy in the land of opportunity. Research in Social Stratification and Mobility, 36, 121–137. doi:10.1016/j.rssm.2014.03.001

>>>>

---
title: "Meritocracy Scale: Preferences and Perceptions"
csl: apa6.csl
bibliography: zlibrary.bib
css: style.css
output:
  pdf_document:
    keep_tex: false
    template: null
    number_sections: true
    toc: true
  html_document:
    theme: flatly
    number_sections: true
    toc: true
    toc_float: true
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
linestretch: '1.5'
link-citations: yes
linkcolor: blue
---

```{r eval=FALSE, echo=FALSE}
# Para obtener doble output (html/pdf) correr directamente en consola/terminal:
rmarkdown::render('index.rmd', output_format = 'all')
```

@@

```{r include=FALSE}
#Determine the output format of the document
outputFormat   = knitr::opts_knit$get("rmarkdown.pandoc.to")

#Figure and Table Caption Numbering, for HTML do it manually
capTabNo = 1; capFigNo = 1;

#Function to add the Table Number
capTab = function(x){
  if(outputFormat == 'html'){
    x = paste0("Table ",capTabNo,". ",x)
    capTabNo <<- capTabNo + 1
  }; x
}

#Function to add the Figure Number
capFig = function(x){
  if(outputFormat == 'html'){
    x = paste0("**","Figura ",capFigNo,": ","**",x)
    capFigNo <<- capFigNo + 1
  }; x
}
```

@@

To measure the ideals of meritocracy, it is essential to differentiate preferences (i.e. what is considered desirable) and perceptions (i.e. how reality is believed to be) [@Duru-bellat2012]. This work focuses on the perceptions of meritocracy.

Although a group of authors has measured the perception of meritocracy as if the perception of inequality of opportunities were the  side opposite of the continuum [@Kunovich2007; @Newman2015], others have shown that both concepts are rather different dimensions [@Reynolds2014]. Following this evidence, we chose to model both constructs as distinct latent variables. Different types of inequalities such as origin, contact or discrimination, cannot be considered in a single factor, since they refer to different realities and perceptions, therefore, it is consistent that they are independent latent variables. We also consider the existence of a latent second order variable, referring to the belief of inequality of opportunities in general.

@@

Additionally, it is important to mention that we will exploratory analysis the relationship between the “get a head” questions and questions that refer to whether “In Chile, people are rewarded or manage to succeed according to different qualities (i.e., hardworking, talented, with contacts)”.

* H1. The perception of meritocracy is a latent variable in the drift of the importance attributed to talent and the effort to get ahead in life.
* H2. Non-meritocratic perception is a latent variable that derives from two elements related to the agreement with the statement that people with contacts and rich parents, manage to get ahead
* H3. Meritocratic preferences behave as a latent variable.
* H4. Non-meritocratic preferences behave as a latent variable.

@@

The present study is of an observational type focused on the measurement of the meritocracy perception variable. This study is part of an experimental study, applied online, which will be longitudinal panel type, that is, the same subjects will be surveyed 3 different occasions. The subjects will be randomly selected to be assigned to a placebo or to either of the two experimental procedures (change of poverty in Chile or international comparison of inequality)
To access the cases we turn to the Netquest survey company, which has coverage in several Latin American countries.

@@

The Sample that will be necessary for this study has not yet been produced, nor has it begun its field work. However, in order to test the online questionnaire and the functionality of the quota offered by the Qualtrics platform, two previous studies have been carried out. The subjects participated in these two opportunities are excluded to the central sample, which corresponds to the 3-wave panel study.
These data from the two pilot studies were used for methodological decisions, descriptive statistics, correlations and confirmation tests.
Due to the above, although the definitive sample has not yet been produced and therefore has not been explored, it is responsible to say, in addition to the review of previous research and international databases, it has some notions of the relationship among the variables product of the analysis of the previous samples

@@

# Variables to use:

All the variables used in the scale use the following question and answer options

* To what extent do you agree or in
disagree with each of the following
affirmations?
    + Strongly disagree
    + Disagree
    + Neither agree nor disagree
    + Agree
    + Totally agree

```{r include=FALSE}
# Get output document type and use as the format argument in kable function
library(knitr)
library(kableExtra)

table_format = if(is_html_output()) {
  "html"
} else if(is_latex_output()) {
  "latex"
}
```

```{r echo=FALSE}

tab01 <- read.csv(file = "materials/table01.csv",header = 1,sep = ";")

cnames <- c("Dimension", "Factor","Statement (english)" , "Statement (spanish)")

caption01 <- capTab("Meritocracy perception and preference")
kable(tab01,format = table_format,booktabs = T, linesep = "",col.names = cnames, caption = caption01) %>%
  kable_styling(full_width = T,latex_options = c("hold_position","scale_down"),position = "center",font_size = 9) %>%
  column_spec(column = 1,width = "1.5cm",) %>%
  column_spec(column = 2,width = "2 cm") %>%
  collapse_rows(columns = 1:2,valign = "middle")

```

@@

# Analysis plan

To evaluate these hypotheses, confirmatory factor analysis (CFA) will be used, since we have strong theory regarding the ordering of the factors. In addition, exploratory factor analysis will be used to evaluate the exploratory hypothesis indicated. The lavaan [@Rosseel2012] R package will be used.

### Inference criteria

The values that will be used as evaluation criteria for the goodness of the adjustment of the model were taken from the proposal of @Brown2008 and are the following:

* Chi-square:> 0.05
* Chi-square ratio:> 3
* Comparative adjustment goodness index (CFI):> 0.95
* Tucker-Lewis Index (TLI):> 0.95
* Root of the average squared residual approximation <0.08.

### Secondary analysis

To evaluate the metric stability of the measurement model [@Davidovetal2014] proposed above we will conduct a longitudinal invariance test using the first and third wave of our study. Following @liuTestingMeasurementInvariance2017, we will test a series of four hierarchical models: Configural, Weak, Strong and Strict invariance models for ordered-categorical indicators based on the assumtion that a five category likert scale cannot be treated as a continous variable because can lead to biased parameter estimates.

@@

### Ethics.
The experiment and survey instruments are approved by the IRB of the University of Chile.

# Bibliography
